Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research

### 2023-12-08 manuscript/paper.Rmd
up

---
title: "Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research"
thanks: "Replication files are available on the author's Github account (http://github.com/svmiller/svm-r-markdown-templates). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com."
subtitle: "Short title goes here!"
author:
- Amos Okutse, Brown University
- Second Author, Another Uni
- Graduate Student, Graduate School
abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec sit amet libero justo. Pellentesque eget nibh ex. Aliquam tincidunt egestas lectus id ullamcorper. Proin tellus orci, posuere sed cursus at, bibendum ac odio. Nam consequat non ante eget aliquam. Nulla facilisis tincidunt elit. Nunc hendrerit pellentesque quam, eu imperdiet ipsum porttitor ut. Interdum et malesuada fames ac ante ipsum primis in faucibus. Suspendisse potenti. Duis vitae nibh mauris. Duis nec sem sit amet ante dictum mattis. Suspendisse diam velit, maximus eget commodo at, faucibus et nisi. Ut a pellentesque eros, sit amet suscipit eros. Nunc tincidunt quis risus suscipit vestibulum. Quisque eu fringilla massa."
keywords: "pandoc, r markdown, knitr"
date: "  `r format(Sys.time(), '%d %B, %Y')` "
geometry: margin=1in
#mainfont: cochineal
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{fvextra}
- \usepackage{float}
- \usepackage{wrapfig}
- \usepackage{amsmath}
- \usepackage{threeparttable} %used to fix table with notes
- \usepackage{float}
- \usepackage{graphicx}
- \usepackage{microtype}
- \usepackage{setspace}
- \usepackage[font=singlespacing]{caption} #can change font here for captions here!!
- \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines, commandchars=\\\{\}}
- \singlespacing
fontsize: 10pt
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    dev: cairo_pdf
    toc: false
    toc_depth: 4
    number_sections: false
    keep_md: false
link-citations: yes
colorlinks: yes
linkcolor: blue
urlcolor: blue
#bibliography: refs.bib
bibliostyle: apalike
editor_options: 
  markdown: 
    wrap: 72
---

@@

Our current analyses combine the 2015 - 2018 NHANES survey cycles to yield $n = 19225$ observations on 35 covariates. This sample size was comprised $n = 9971$ and $n = 9254$ observations from the 2015/2016 and 2017/2018 survey cycles, respectively. Analyses excluded individuals with missing data on sleep ($n = 6818$), blood pressure (BP) (n = 1055), and body mass index (BMI) or those with BMI > 25 kg/$m^2$ (overweight) (n = 5521). Individuals that reported being on anti-hypertensive medication were also excluded from further analyses (n = 2944).

### Outcome definition: 
The outcome is

@@

### Exposure:
Sleep duration on workdays was evaluated by the questionnaire with the following questions:
“Number of hours usually sleep on weekdays or workdays”. Sleep duration was divided into three groups, which
were < 6 h, 6–8 h, ≥ 8 h respectively, of which 6–8 h was used as the reference group.

@@

<div id="refs"></div>

>>>>

---
title: "Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research"
thanks: "Replication files are available on the author's Github account (http://github.com/svmiller/svm-r-markdown-templates). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com."
subtitle: "Short title goes here!"
author:
- Amos Okutse, Brown University
- Second Author, Another Uni
- Graduate Student, Graduate School
abstract: "**Introduction:** Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec sit amet libero justo. Pellentesque eget nibh ex. Aliquam tincidunt egestas lectus id ullamcorper.

**Methods:** Proin tellus orci, posuere sed cursus at, bibendum ac odio. Nam consequat non ante eget aliquam. Nulla facilisis tincidunt elit. Nunc hendrerit pellentesque quam, eu imperdiet ipsum porttitor ut. Interdum et malesuada fames ac ante ipsum primis in faucibus. Suspendisse potenti. Duis vitae nibh mauris. Duis nec sem sit amet ante dictum mattis. Suspendisse diam velit, maximus eget commodo at, faucibus et nisi. Ut a pellentesque eros, sit amet suscipit eros. Nunc tincidunt quis risus suscipit vestibulum. Quisque eu fringilla massa."
keywords: "pandoc, r markdown, knitr"
date: "  `r format(Sys.time(), '%d %B, %Y')` "
geometry: margin=1in
#mainfont: cochineal
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{fvextra}
- \usepackage{float}
- \usepackage{wrapfig}
- \usepackage{amsmath}
- \usepackage{threeparttable} %used to fix table with notes
- \usepackage{float}
- \usepackage{graphicx}
- \usepackage{microtype}
- \usepackage{setspace}
- \usepackage[font=singlespacing]{caption} #can change font here for captions here!!
- \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines, commandchars=\\\{\}}
- \singlespacing
fontsize: 10pt
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    dev: cairo_pdf
    toc: false
    toc_depth: 4
    number_sections: false
    keep_md: false
link-citations: yes
colorlinks: yes
linkcolor: blue
urlcolor: blue
#bibliography: refs.bib
bibliostyle: apalike
editor_options: 
  markdown: 
    wrap: 72
---

@@

Our current analyses combine the 2015 - 2018 NHANES survey cycles to
yield $n = 19225$ observations on 35 covariates. This sample size was
comprised $n = 9971$ and $n = 9254$ observations from the 2015/2016 and
2017/2018 survey cycles, respectively. Analyses excluded individuals
with missing data on sleep ($n = 6818$), blood pressure (BP) (n = 1055),
and body mass index (BMI) or those with BMI \> 25 kg/$m^2$ (overweight)
(n = 5521). Individuals that reported being on anti-hypertensive
medication were also excluded from further analyses (n = 2944).

### Outcome definition:

The outcome is

@@

### Exposure:

Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". Sleep duration was divided into three groups, which were \< 6
h, 6--8 h, ≥ 8 h respectively, of which 6--8 h was used as the reference
group.

@@

::: {#refs}
:::
